\documentclass[11pt]{article}

\usepackage[margin=0.7in]{geometry}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage{xcolor}
\usepackage{hyperref}
\usepackage{parskip}
\usepackage{tcolorbox}
\usepackage{array}

\hypersetup{colorlinks=true, linkcolor=black, urlcolor=blue!60!black}

\definecolor{accent}{RGB}{20,90,120}
\definecolor{ph}{RGB}{150,120,40}

\titleformat{\section}{\large\bfseries\color{accent}}{\thesection.}{0.5em}{}
\titlespacing\section{0pt}{6pt}{2pt}

\newcommand{\fillin}[1]{{\color{ph}\textit{[#1]}}}

\setlist[itemize]{leftmargin=1.3em, topsep=1pt, itemsep=0.5pt}
\renewcommand{\arraystretch}{1.05}

\begin{document}

\begin{center}
{\Large\bfseries Sprint 1 --- Team Report}\\[3pt]
{\normalsize Indigenomics Capstone --- exploring a public-facing companion to Indigenomics AI}
\end{center}

\vspace{2pt}
\noindent\begin{tabular}{@{}p{0.5\textwidth}p{0.46\textwidth}@{}}
\textbf{Sprint:} 1 (Week 4) --- Discovery / Direction-Selection & \textbf{Timebox:} 1 week \\
\textbf{Team:} En-Ping Su, Tong Wu, Shiting Huang, Mengshan Li & \textbf{Sprint Lead (Scrum Master + acting PO):} En-Ping Su \\
\textbf{Dates:} Jun 1 -- Jun 8, 2026 (Mon--Mon) & \\
\end{tabular}

\hrule
\vspace{2pt}

\section{Sprint goal \& why a discovery sprint}
The product is not yet scope-locked --- we are still aligning with the client (Indigenomics) on what to build, and \textbf{do not yet have a green light} on any single direction. Rather than treat that as a blocker, we made the uncertainty the work. \textbf{Sprint goal: narrow the capstone direction with evidence and validate it with the client, leaving Sprint 2 ready to build a vertical slice.}

\textit{Note on metrics:} with no velocity baseline in Sprint 1, we tracked discovery and reliability metrics (Section 4) and only \emph{baselined} velocity for Sprint 2 --- reporting a velocity number now would be meaningless.

\section{Exploration to date (all directions, including ones the client declined)}
The project has moved through three strands. We show all of them --- including the idea the client declined --- because each fed the next, and the engineering carries forward.

\smallskip
{\footnotesize
\noindent\begin{tabular}{@{}p{0.022\textwidth}p{0.245\textwidth}p{0.145\textwidth}p{0.30\textwidth}p{0.155\textwidth}@{}}
\hline
\textbf{\#} & \textbf{Direction} & \textbf{Client stance} & \textbf{Evidence / artifacts} & \textbf{Status} \\
\hline
1 & \textbf{Educational platform} --- citation-first educational tool over open data (was ``E1''); \emph{our first idea} & \textbf{Not keen} & Deck4 pitch + feasibility, script, internal report (\texttt{Project/}) & Set aside \\
2 & \textbf{Consent Layers} --- consent/confirmation app, built at the Indigenomics \textbf{Tech Jam} & Built on their turf; exploratory & App + reusability audit (\texttt{06\_\dots}; \texttt{Tech Jam/}) & Foundation --- engine carries into \#3 \\
3 & \textbf{RAP platform} --- consent-based, Indigenous-governed infrastructure for \emph{verified} economic data; supplier-confirmed RAP questionnaire, RAP Index as first output & \textbf{No green light yet} & MVP design + RAP reference docs (\texttt{Week 4/}: mockup, brochure, survey guide) & Active exploration \\
--- & \textbf{Deck comparators} --- hero sim, conversational entry, reference layer, personal tools, B2B directory & Their original menu & \texttt{01\_Product\_Backlog.md} (E3--E8) & Parked \\
\hline
\end{tabular}}

\smallskip
\noindent\textbf{The through-line:} the educational platform did not land with the client, but the \textbf{Consent Layers} work from the Tech Jam produced a confirmation engine we could reuse --- exactly what the \textbf{RAP platform} needs to let a named Indigenous supplier confirm each economic-data entry. A declined idea and a ``tangential'' hackathon both became load-bearing inputs to the direction we now explore.

\section{Roles \& artifacts}
The lead role rotates each sprint (En-Ping Su $\rightarrow$ Mengshan Li $\rightarrow$ Shiting Huang $\rightarrow$ Tong Wu $\rightarrow$ showcase). Artifacts produced/used this sprint:
\begin{itemize}
  \item \textbf{Product backlog, sprint backlog \& task board} --- \textbf{Jira} Scrum board (burndown / velocity / cumulative-flow from built-in reports): \url{https://indigenomics-capstone.atlassian.net/jira/software/projects/RAP/boards/1}
  \item \textbf{Sprint Goal + Definition of Done}; \textbf{client questionnaire}; \textbf{risk/blocker log}; \textbf{direction scorecard}; \textbf{retrospective}
  \item \textbf{Decision inputs:} data-feasibility memo (Mengshan Li) and consent-layer reusability audit (Shiting Huang)
\end{itemize}

\section{What each member did}
\noindent RAP-platform ownership going forward: \textbf{backend} --- Shiting Huang, Mengshan Li; \textbf{frontend + client} --- Tong Wu, En-Ping Su.

\nopagebreak
{\footnotesize
\noindent\begin{tabular}{@{}p{0.15\textwidth}p{0.23\textwidth}p{0.56\textwidth}@{}}
\hline
\textbf{Member} & \textbf{Role} & \textbf{Contribution this sprint} \\
\hline
En-Ping Su & Sprint Lead · Frontend / Client & Backlog + Goal/DoD; ran client check-in + questionnaire; risk log; authored Direction Decision memo \\
Tong Wu & Frontend / UX + Client & Clickable RAP-platform mockup (Data Portal); client communication; captured requirements into backlog \\
Shiting Huang & Backend / Eng.\ · Arch. & Consent-layer reusability audit; mapped the confirmation engine onto the RAP platform; repo + CI + dev env \\
Mengshan Li & Backend / Data · Feasibility & Data-feasibility memo --- verified RAP/procurement/RAP-survey data sources; go/no-go table \\
\hline
\end{tabular}}

\section{Metrics \& results}
\noindent\begin{tabular}{@{}p{0.6\textwidth}p{0.36\textwidth}@{}}
\hline
\textbf{Metric} & \textbf{Result} \\
\hline
Sprint goal met? & \fillin{Yes / Partly / No} \\
Commitment reliability (done $\div$ committed) & \fillin{\_\_ / \_\_ = \_\_\%} \\
Avg.\ cycle time per card & \fillin{\_\_ h} \\
Assumptions validated / invalidated & \fillin{\_\_} \\
Client questions resolved & \fillin{\_\_ / 11} \\
Directions evaluated & 3 strands + deck comparators \\
Risks closed (esp.\ scope) & \fillin{\_\_ / 4} \\
\hline
\end{tabular}

\smallskip
\noindent\fillin{1--2 sentences interpreting the numbers --- e.g.\ what the burndown showed, where cycle time bunched.}

\section{Outcome --- current direction (not yet greenlit)}
\textbf{Leading direction:} \textbf{RAP platform} --- pending client confirmation; presented as our best candidate, not committed scope.\\
\textbf{Why (evidence):} The Consent Layers confirmation engine gives the RAP platform a real head start (see \texttt{06\_\dots}); the educational platform was set aside after the client was not keen; and open RAP/procurement data makes the supplier-confirmation slice feasible without partner-gated data. \fillin{Add: scorecard total + the client's answer to Q2 once recorded.}\\
\textbf{Sprint 2 setup:} lead = Mengshan Li; focus = thin vertical slice of the RAP confirmation flow; gating items carried = \fillin{client green light; resolve consent-app LICENSE / spec review; advisor confirmation}.

\section{Retrospective (summary)}
\begin{itemize}
  \item \textbf{Went well:} \fillin{\dots}
  \item \textbf{Didn't:} \fillin{\dots}
  \item \textbf{Change next sprint:} \fillin{action --- owner --- by}
\end{itemize}

\vfill
\noindent\rule{\textwidth}{0.3pt}\\
{\small\textit{Appendices (not counted toward the 2 pages): board export, data-feasibility memo, consent-layer reusability audit (\texttt{06\_\dots}), Deck4 review \& feasibility (\texttt{Project/}), RAP platform mockup + RAP reference docs (\texttt{Week 4/}), prototype recordings (linked, not embedded). The per-person 1-pager (hours + AI value-add) is submitted separately, one per member.}}

\end{document}
